---
title: "Exploratory Data Analysis"
author: "Chance Robinson"
date: "11/2/2019"
output: 
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Exploratory Data Analysis

## Library Imports


```{r library-imports, quietely=TRUE, warn.conflicts=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
# Correlation Matrix
library(ggcorrplot)
library(Hmisc)
# Downsampling
library(caret)
```

## Load the CSV Data

```{r load-data}
train <- read.csv("../../../../data/train_V2.csv", stringsAsFactors=FALSE)
test <- read.csv("../../../../data/test_V2.csv", stringsAsFactors=FALSE)

```


## Default Output


### Data Dictionary

  Column Name      |Type                  |Description
  -----------------|----------------------|-------------------------------------------------
  DBNOs            |Integer               |Number of enemy players knocked.
  assists          |Integer 		          |Number of enemy players this player damaged that were killed by teammates.
  boosts           |Integer               |Number of boost items used.
  damageDealt      |Float 			          |Total damage dealt. Note: Self inflicted damage is subtracted.
  headshotKills    |Integer               |Number of enemy players killed with headshots.
  heals            |Integer               |Number of healing items used.
  Id               |Character             |Player’s Id
  killPlace        |Integer               |Ranking in match of number of enemy players killed.
  killPoints       |Integer               |Kills-based external ranking of player.
  killStreaks      |Integer               |Max number of enemy players killed in a short amount of time.
  kills            |Integer               |Number of enemy players killed.
  longestKill      |Float 			          |Longest distance between player and player killed at time of death. 
  matchDuration    |Integer               |Duration of match in seconds.
  matchId          |Character             |ID to identify match. There are no matches that are in both the training and testing set.
  matchType        |Character             |String identifying the game mode that the data comes from. 
  rankPoints       |Integer               |Elo-like ranking of player. 
  revives          |Integer               |Number of times this player revived teammates.
  rideDistance     |Float                 |Total distance traveled in vehicles measured in meters.
  roadKills        |Integer               |Number of kills while in a vehicle.
  swimDistance     |Float                 |Total distance traveled by swimming measured in meters.
  teamKills        |Integer               |Number of times this player killed a teammate.
  vehicleDestroys  |Integer               |Number of vehicles destroyed.
  walkDistance     |Float                 |Total distance traveled on foot measured in meters.
  weaponsAcquired  |Integer               |Number of weapons picked up.
  winPoints        |Integer               |Win-based external ranking of player. 
  groupId          |Character             |ID to identify a group within a match. If the same group of players plays in different matches, they will have a different groupId each time.
  numGroups        |Integer               |Number of groups we have data for in the match.
  maxPlace         |Integer               |Worst placement we have data for in the match. This may not match with numGroups, as sometimes the data skips over placements.
  winPlacePerc     |Float                 |The target of prediction. This is a percentile winning placement, where 1 corresponds to 1st place, and 0 corresponds to last place in the match. 



### Identify Dimensions
 
```{r train-dimensions}
dim(train)
```


### Train Columns

```{r train-columns}
colnames(train)
```


```{r head-train}
head(train)
# summary(train)
# str(train)
# dim(train)
```



```{r head-test}
head(test)
# summary(test)
# str(test)
# dim(test)
```


### Describe the Data Types


```{r train-describe}
str(train)
```


#### Missing Values

```{r train-missing}
df_na_winPlacePerc <- train %>%
  filter(is.na(winPlacePerc)) 

df_na_winPlacePerc

# remove the row with no winPlacePerc   
train <- train[!train$Id == 'f70c74418bb064',]

```


### Numeric Columns


#### Column Names

```{r train-numeric}


train.numeric <- train %>%
  select_if(is.numeric)

colnames(train.numeric)

```

#### Summary Tables

```{r train-numeric-summary}

summary(train.numeric)

```





### Non-Numeric Columns

#### Column Names

```{r train-non-numeric}


train.non.numeric <- train %>%
  select_if(is.character)

colnames(train.non.numeric)

```


#### Count by Match Type

* FPP - First Person Perspective
* TPP - Third Peron Perspective

```{r}
train.non.numeric %>%
  group_by(matchType) %>%
  ggplot(aes(x = matchType, color=matchType)) + 
  geom_bar() +
  geom_text(stat='count', aes(label=..count..), vjust=-1) +
  ggtitle("Count by Match Type") +
  labs(x = "Match Type", y = "Count") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none")
```



## Correlation Matrix


```{r train-numeric-cor-matrix}

# gc()

# memory.size(max = FALSE)
# memory.limit(size = NA)

corr <- round(cor(train.numeric), 1)
  
ggcorrplot(corr, method = "square", type = "full", lab = TRUE)

```


###Correlation matrix for quantitative data

```{r corr-matrix}
# function for flattening and ordering the correlation matrix
flattenCorrMatrix <- function(cormat, pmat) {
  ut <- upper.tri(cormat)
  data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor  =(cormat)[ut],
    p = pmat[ut]
    )
}


# See what variables are correlated with each other, p-values
correlation.matrix <- rcorr(as.matrix(train.numeric))
corDF <- data.frame(flattenCorrMatrix(correlation.matrix$r, correlation.matrix$P))

# Order the correlation matrix to show the highest correlated
# data.frame(corDF[order(-corDF$cor),])
quantDataModel <- corDF[which(corDF$cor >= 0.4),]
data.frame(quantDataModel[order(-quantDataModel$cor),])

```

```{r train-add-top-10}
train.mod <- train

train.mod <- train.mod %>%
  filter(matchType %in% c("solo", "solo-fpp")) %>%
  mutate(top.10 = ifelse(winPlacePerc>.9, 1, 0))


```



```{r train-downsampled}

train.mod.ds <- downSample(train.mod, as.factor(train.mod$top.10), list = FALSE)

```




```{r train.mod.ds-logistic.regression-model}

model <- glm(top.10~walkDistance+killPlace+boosts+weaponsAcquired+damageDealt+heals+kills, data = train.mod.ds)
summary(model)
confint(model) 
```


```{r train-confusion-matrix}

train.mod.ds$predict <- ifelse(model$fitted.values >0.5, 1, 0)

mytable <- table(train.mod.ds$top.10, train.mod.ds$predict)
rownames(mytable) <- c("Obs (Bottom 90)", "Obs (Top 10)")
colnames(mytable) <- c("Pred (Bottom 90)","Pred (Top 10)")
mytable

```

#### Accuracy
```{r model-accuracy}
# Overall performance of our prediction model
accuracy <- sum(diag(mytable))/sum(mytable)
accuracy


tn <- mytable[1,1]
fn <- mytable[2,1]
fp <- mytable[1,2]
tp <- mytable[2,2]

rtotal.0 <- sum(mytable[1,])
rtotal.1 <- sum(mytable[2,])
ctotal.0 <- sum(mytable[,1])
ctotal.1 <- sum(mytable[,2])
total <- sum(mytable)


tn
fn
fp
tp

```

#### Sensitivity

* When it was in the top 10%, how often did we predict that it was?

```{r model-sensitivity}
# True Positive Rate
sensitivity <- (tp) / (ctotal.1)
sensitivity

```

#### Specificity

* When it was in the bottom 90%, how often did we predict that it was?

```{r model-specificity}
# True Negative Rate:
specificity <- (tn) / (rtotal.0)
specificity

```

#### Precision

* When we predicted yes, how often is it correct?

```{r model-precision}
# True Negative Rate:
precision <- (tp) / (ctotal.1)
precision

```



```{r train-numeric-pca}


cols.to.remove <- c("DBNOs", "revives")

train.mod.numeric <- train.mod %>%
  filter(matchType %in% c("solo", "solo-fpp")) %>%
  select_if(is.numeric) %>%
  select(-cols.to.remove) %>%
  mutate(top.10 = ifelse(winPlacePerc>.9, 1, 0)) %>%
  mutate(matchDurationLength = ifelse(matchDuration >= mean(matchDuration), 1, 0))


head(train.mod.numeric)

# table(train.mod.numeric$revives)


pca.result <- prcomp(train.mod.numeric[1:22], scale.=TRUE)
# pca.result <- prcomp(train.mod.numeric[1:24])
pca.scores <- pca.result$x

head(pca.scores)
# pairs(pca.scores)
# cor(pca.scores)
```


A scree plot of the eigenvalues used to determine how many pc's to keep can be plotted in the following way:
```{r}
par(mfrow=c(1,2))
eigenvals <- (pca.result$sdev)^2
plot(1:22,eigenvals/sum(eigenvals), type="l", main="Scree Plot", ylab="Prop. Var. Explained")
cumulative.prop <- cumsum(eigenvals/sum(eigenvals))
plot(1:22,cumulative.prop, type="l", main="Cumulative proportion", ylim=c(0,1))
par(mfrow=c(1,1))

```


```{r}
#Getting a look at the distribution
table(train.mod.numeric$top.10)

#Adding the response column to the PC's data frame
pca.scores <- data.frame(pca.scores)
pca.scores$top.10 <- as.factor(train.mod.numeric$top.10)
pca.scores$matchDurationLength <- as.factor(train.mod.numeric$matchDurationLength)

table(train.mod.numeric$matchDurationLength)

# ggplot(data = pca.scores, aes(x = PC1, y = PC2)) +
#   geom_point(aes(col=top.10), size=1)+
#   ggtitle("PCA of PUBG Top 10%")


```



```{r}

# , shape = matchDurationLength

plotPC <- function(mydata) {
  sampleData <- sample_frac(mydata, 0.10)
  ggplot(data = sampleData, aes(x = PC1, y = PC2)) +
    geom_point(aes(col=top.10), size=1)+
    ggtitle("PCA of PUBG Top 10% Placement")
}

set.seed(314159)
plotPC(pca.scores)


```




