---
title: "Exploratory Data Analysis"
author: "Chance Robinson"
date: "11/2/2019"
output: 
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Exploratory Data Analysis

## Library Imports


```{r library-imports, quietely=TRUE, warn.conflicts=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
# Correlation Matrix
library(ggcorrplot)
library(Hmisc)
# Downsampling
library(caret)
```

## Load the CSV Data

```{r load-data}

data <- read.csv("../../../../data/pubg_solo_game_types.csv", stringsAsFactors=FALSE)
train.full <- read.csv("../../../../data/pubg_solo_game_types_train_full.csv", stringsAsFactors=FALSE)

train <- read.csv("../../../../data/pubg_solo_game_types_train_downsampled.csv", stringsAsFactors=FALSE)
test <- read.csv("../../../../data/pubg_solo_game_types_test_full.csv", stringsAsFactors=FALSE)


```



```{r train-test-split}

train.mod <- train
#
train.mod <- train.mod %>%
  filter(matchType %in% c("solo")) %>%
  mutate(top.10 = ifelse(winPlacePerc>.9, 1, 0)) 
  # mutate(top.10 = as.factor(top.10))


set.seed(1234)
train.indices <- createDataPartition(y = train.mod$top.10,p = 0.7,list = FALSE)
train.full <- train.mod[train.indices,]
test.full <- train.mod[-train.indices,]

# 
train.downsampled <- downSample(train.full, train.full$top.10)
train.downsampled$Class <- NULL

# head(train.downsampled)
#
# dim(train.mod)
# dim(train.full)
# dim(test.full)
# dim(train.downsampled)

# write.csv(train.mod, "C:\\Users\\Chance\\pubg_solo_game_types.csv", row.names=FALSE)
# write.csv(train.full, "C:\\Users\\Chance\\pubg_solo_game_types_train_full.csv", row.names=FALSE)
# write.csv(train.downsampled, "C:\\Users\\Chance\\pubg_solo_game_types_train_downsampled.csv", row.names=FALSE)
# write.csv(test.full, "C:\\Users\\Chance\\pubg_solo_game_types_test_full.csv", row.names=FALSE)
# # 

#data <- read.csv("../../../../data/pubg_solo_game_types.csv", stringsAsFactors=FALSE)


```

## Default Output


### Data Dictionary

  Column Name      |Type                  |Description
  -----------------|----------------------|-------------------------------------------------
  DBNOs            |Integer               |Number of enemy players knocked.
  assists          |Integer 		          |Number of enemy players this player damaged that were killed by teammates.
  boosts           |Integer               |Number of boost items used.
  damageDealt      |Float 			          |Total damage dealt. Note: Self inflicted damage is subtracted.
  headshotKills    |Integer               |Number of enemy players killed with headshots.
  heals            |Integer               |Number of healing items used.
  Id               |Character             |Player’s Id
  killPlace        |Integer               |Ranking in match of number of enemy players killed.
  killPoints       |Integer               |Kills-based external ranking of player.
  killStreaks      |Integer               |Max number of enemy players killed in a short amount of time.
  kills            |Integer               |Number of enemy players killed.
  longestKill      |Float 			          |Longest distance between player and player killed at time of death. 
  matchDuration    |Integer               |Duration of match in seconds.
  matchId          |Character             |ID to identify match. There are no matches that are in both the training and testing set.
  matchType        |Character             |String identifying the game mode that the data comes from. 
  rankPoints       |Integer               |Elo-like ranking of player. 
  revives          |Integer               |Number of times this player revived teammates.
  rideDistance     |Float                 |Total distance traveled in vehicles measured in meters.
  roadKills        |Integer               |Number of kills while in a vehicle.
  swimDistance     |Float                 |Total distance traveled by swimming measured in meters.
  teamKills        |Integer               |Number of times this player killed a teammate.
  vehicleDestroys  |Integer               |Number of vehicles destroyed.
  walkDistance     |Float                 |Total distance traveled on foot measured in meters.
  weaponsAcquired  |Integer               |Number of weapons picked up.
  winPoints        |Integer               |Win-based external ranking of player. 
  groupId          |Character             |ID to identify a group within a match. If the same group of players plays in different matches, they will have a different groupId each time.
  numGroups        |Integer               |Number of groups we have data for in the match.
  maxPlace         |Integer               |Worst placement we have data for in the match. This may not match with numGroups, as sometimes the data skips over placements.
  winPlacePerc     |Float                 |The target of prediction. This is a percentile winning placement, where 1 corresponds to 1st place, and 0 corresponds to last place in the match. 



### Identify Dimensions

```{r data-dimensions-data}
dim(data)
```


```{r data-dimensions-data-2}
table(data$top.10)
```


```{r data-dimensions-train-full}
dim(train.full)

```


```{r data-dimensions-train}
# dim(train)
# 
# train[train$Id == '8d699d579f43e1']
```


```{r data-dimensions-test}
dim(test)
```


### Train Columns

```{r data-columns}
colnames(data)
```


```{r head-data}
# head(data)

```


### Describe the Data Types


```{r train-describe}
str(data)
```


#### Missing Values

```{r train-missing}
# df_na_winPlacePerc <- train %>%
#   filter(is.na(winPlacePerc)) 
# 
# df_na_winPlacePerc
# 
# # remove the row with no winPlacePerc   
# train <- train[!train$Id == 'f70c74418bb064',]

```


### Numeric Columns


#### Column Names

```{r data-numeric}


data.numeric <- data %>%
  select_if(is.numeric)

colnames(data.numeric)

```

#### Summary Tables

```{r data-numeric-summary}

summary(data.numeric)

```





### Non-Numeric Columns

#### Column Names

```{r data-non-numeric}


data <- train %>%
  select_if(is.character)

colnames(data)

```


## Correlation Matrix


```{r train-numeric-cor-matrix, fig.height = 10, fig.width = 10, fig.align = "center", message=FALSE, error=FALSE, warning=FALSE}

# gc()

# memory.size(max = FALSE)
# memory.limit(size = NA)

corr <- round(cor(data.numeric), 1)
  
ggcorrplot(corr, method = "square", type = "full", lab = TRUE)

```


###Correlation matrix for quantitative data

```{r corr-matrix}
# function for flattening and ordering the correlation matrix
flattenCorrMatrix <- function(cormat, pmat) {
  ut <- upper.tri(cormat)
  data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor  =(cormat)[ut],
    p = pmat[ut]
    )
}


# See what variables are correlated with each other, p-values
correlation.matrix <- rcorr(as.matrix(data.numeric))
corDF <- data.frame(flattenCorrMatrix(correlation.matrix$r, correlation.matrix$P))

# Order the correlation matrix to show the highest correlated
# data.frame(corDF[order(-corDF$cor),])
quantDataModel <- corDF[which(abs(corDF$cor) >= 0.6),]
data.frame(quantDataModel[order(-abs(quantDataModel$cor)),])

```


```{r }
cols_to_remove = c("Id", "groupId", "matchId", "matchType", "DBNOs", "revives", "rankPoints", "winPoints", "killPoints", "winPlacePerc")

train.mod <- train %>%
  select(-cols_to_remove) %>%
  mutate(top.10 = factor(top.10, labels = c("No", "Yes"))) 


# head(train.mod)


```


### Histogram of Assists (1)

Number of enemy players this player damaged that were killed by teammates.

```{r}
train.mod %>%
  ggplot(aes(assists)) + 
  geom_bar() +
  facet_wrap(~ top.10) + 
  ggtitle("Histogram of Assists by Top 10%") 

```


### Histogram of Boosts (2)

Number of boost items used.

```{r}
train.mod %>%
  ggplot(aes(boosts)) + 
  geom_bar() +
  facet_wrap(~ top.10) + 
  ggtitle("Histogram of Boosts by Top 10%") 

```


### Histogram of Damage Dealt (3)

Total damage dealt. Note: Self inflicted damage is subtracted.

```{r}
train.mod %>%
  ggplot(aes(damageDealt)) + 
  geom_histogram(binwidth = 50) +
  facet_wrap(~ top.10) + 
  ggtitle("Histogram of Damage Dealt by Top 10%") 

```


### Histogram of Head Shot Kills (4)

Number of enemy players killed with headshots.

```{r}
train.mod %>%
  ggplot(aes(headshotKills)) + 
  geom_bar() +
  facet_wrap(~ top.10) + 
  ggtitle("Histogram of Head Shot Kills by Top 10%") 

```


### Histogram of Heals (5)

Number of healing items used.

```{r}
train.mod %>%
  ggplot(aes(heals)) + 
  geom_bar() +
  facet_wrap(~ top.10) + 
  ggtitle("Histogram of Heals by Top 10%") 

```

### Histogram of Kill Place (6)

Ranking in match of number of enemy players killed.

* Note that the Top 10% of Players never go above 50

```{r}
train.mod %>%
  ggplot(aes(killPlace)) + 
  geom_histogram(binwidth = 5) +
  facet_wrap(~ top.10) + 
  ggtitle("Histogram of Kill Place by Top 10%") 

```



### Histogram of Kills  (7)

Number of enemy players killed.


```{r}
train.mod %>%
  ggplot(aes(kills)) + 
  geom_bar() +
  facet_wrap(~ top.10) + 
  ggtitle("Histogram of Kills by Top 10%") 

```



### Histogram of Kill Streaks  (8)

Max number of enemy players killed in a short amount of time.


```{r}
train.mod %>%
  ggplot(aes(killStreaks)) + 
  geom_bar() +
  facet_wrap(~ top.10) + 
  ggtitle("Histogram of Kill Streaks by Top 10%") 

```


### Histogram of Longest Kill (9)

Longest distance between player and player killed at time of death. This may be misleading, as downing a player and driving away may lead to a large longestKill stat.


```{r}
train.mod %>%
  ggplot(aes(longestKill )) + 
  geom_histogram(binwidth = 25) +
  facet_wrap(~ top.10) + 
  ggtitle("Histogram of Longest Kill by Top 10%") 

```


### Histogram of Match Duration (10)

Duration of match in seconds.

```{r}
train.mod %>%
  ggplot(aes(matchDuration)) + 
  geom_histogram(binwidth = 10) +
  # facet_wrap(~ top.10) + 
  ggtitle("Histogram of Match Duration") 

```


### Histogram of maxPlace (11)

Worst placement we have data for in the match. This may not match with numGroups, as sometimes the data skips over placements.


```{r}
train.mod %>%
  ggplot(aes(maxPlace)) + 
  geom_bar() +
  facet_wrap(~ top.10) + 
  ggtitle("Histogram of maxPlace by Top 10%") 

```


### Histogram of numGroups (12)

Number of groups we have data for in the match.


```{r}
train.mod %>%
  ggplot(aes(numGroups)) + 
  geom_bar() +
  facet_wrap(~ top.10) + 
  ggtitle("Histogram of numGroups by Top 10%") 

```



### Histogram of Ride Distance (13)

Total distance traveled in vehicles measured in meters.

```{r}
train.mod %>%
  ggplot(aes(rideDistance )) + 
  geom_histogram() +
  facet_wrap(~ top.10) + 
  ggtitle("Histogram of Ride Distance by Top 10%") 

```


### Histogram of weapons Acquired (14)

Number of weapons picked up.

```{r}
train.mod %>%
  ggplot(aes(weaponsAcquired)) + 
  geom_histogram(binwidth = 1) +
  facet_wrap(~ top.10) + 
  ggtitle("Histogram of Weapons Acquired by Top 10%") 

```



```{r}

pca.result <- prcomp(train.mod[1:18], scale.=TRUE)
std_dev <- pca.result$sdev
pr_var <- std_dev^2
prop_varex <- pr_var / sum(pr_var)
sum(prop_varex[1:15])


plot(cumsum(prop_varex))


```



```{r}

# metric <- "Accuracy"
# control <- trainControl(method = "repeatedcv", number = 10, repeats = 3)
# mtry <- sqrt(ncol(train.mod))
# tunegrid <- expand.grid(.mtry=mtry)

```

```{r}

# model.rf <- train(top.10~., data=train.mod, method="rf", metric=metric, tunegrid=tunegrid, trControl=control)
```



#### Sensitivity

* When it was in the top 10%, how often did we predict that it was?

#### Specificity

* When it was in the bottom 90%, how often did we predict that it was?

#### Precision

* When we predicted yes, how often is it correct?


